Data Munging

### 2020-10-08 scripts/dataMunge.Rmd
Updated input data file.

```{r}
# Read dissolved gas data file
dg <- read.table(file = paste0(localPath, 
                               "/Environmental Protection Agency (EPA)/",
                               "ORD NLA17 Dissolved Gas - Documents/",
                               "inputData/nla17gasDataAggregated_2020-10-07.txt"),
                 header = TRUE, sep = "\t", as.is = TRUE) 
```

>>>>

```{r}
# Read dissolved gas data file
dg <- read.table(file = paste0(localPath, 
                               "/Environmental Protection Agency (EPA)/",
                               "ORD NLA17 Dissolved Gas - Documents/",
                               "inputData/nla17gasDataAggregated_2020-10-08.txt"),
                 header = TRUE, sep = "\t", as.is = TRUE) 
```
